Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-09 sections/introduction.tex
changed the labels in the text, too

The resolution of SICM is determined by the inner opening radius
$r_\mathrm{i}$ of the scanning pipette and can be approximated as
$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}A)
\cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
only limited by the technical limits to produce pipettes with very small
openings. Pipettes with radii of approximately 6.75\,nm have been used in for
SICM imaging (Fig.~\ref{fig:sicm-resolution}B) \cite{Shevchuk2008}. In
contrast, the resolution in light microscopy is fundamentally limited by the
diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
be focused to a spot smaller than the resolution limit $d_\text{min}$
\cite{Abbe1873}:
\begin{equation}
  d_\text{min} = \frac\lambda{2n\sin\alpha} = \frac\lambda{2\mathrm{NA}}\text{.}
  \label{eq:diffraction-limit}
\end{equation}
Here, $\lambda$ denotes the wavelength of the light used to generate the
image, $n$ the diffractive index of the medium between sample and objective
lense and $\alpha$ the half-cone opening angle of the objective lense. The
product $n\sin\alpha$ is called the numerical aperture $\mathrm{NA}$ of the
objective. The exact limit, of course, depends on $\lambda$ and the NA of the
objective, but as a rule of thumb, it is often stated that the resolution
limit is in the range of 200\,nm. This is approximately 14 times the size of
the smallest structures observed in the SICM recordings shown in
Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
\cite{Shevchuk2008}.

\begin{figure}
  \sidecaption
  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
      spermatozoon.} \textbf{a:} Proteins A and B in the stable structures
    observed by SICM. \textbf{b:} Hypothetical positions of the fluorescent
    labels of proteins A and B. Scale bar: 200\,nm \textbf{c:} Computed
    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
    for the green marker.}
  \label{fig:sicm-and-light-resolution}
\end{figure}
In all stable structures in the recordings (highlighted by the dashed lines)
at least one group of three protrusions arranged in a line are observable. To
exemplify the impact of the limited resolution of light microscopy, assume,
without any biological support, that such a complex is comprised of two
different proteins A and B, which float in the plasma membrane until they form
the complex. In the complex, protein A is located at the first and last
position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
protein B on the central spot (green arrows in
Fig.~\ref{fig:sicm-and-light-resolution}A). Further, assume that the two
different proteins have been labelled by two different fluorescent markers
(the positions of the markers are indicated by the magenta and green dots in
Fig.~\ref{fig:sicm-and-light-resolution}B) and a correlating light microscopic
image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}C) to analyze
the molecular composition of the stable structures.

>>>>

The resolution of SICM is determined by the inner opening radius
$r_\mathrm{i}$ of the scanning pipette and can be approximated as
$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}a)
\cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
only limited by the technical limits to produce pipettes with very small
openings. Pipettes with radii of approximately 6.75\,nm have been used in for
SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2008}. In
contrast, the resolution in light microscopy is fundamentally limited by the
diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
be focused to a spot smaller than the resolution limit $d_\text{min}$
\cite{Abbe1873}:
\begin{equation}
  d_\text{min} = \frac\lambda{2n\sin\alpha} = \frac\lambda{2\mathrm{NA}}\text{.}
  \label{eq:diffraction-limit}
\end{equation}
Here, $\lambda$ denotes the wavelength of the light used to generate the
image, $n$ the diffractive index of the medium between sample and objective
lense and $\alpha$ the half-cone opening angle of the objective lense. The
product $n\sin\alpha$ is called the numerical aperture $\mathrm{NA}$ of the
objective. The exact limit, of course, depends on $\lambda$ and the NA of the
objective, but as a rule of thumb, it is often stated that the resolution
limit is in the range of 200\,nm. This is approximately 14 times the size of
the smallest structures observed in the SICM recordings shown in
Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
\cite{Shevchuk2008}.

\begin{figure}
  \sidecaption
  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
      spermatozoon.} \textbf{a:} Proteins A and B in the stable structures
    observed by SICM. \textbf{b:} Hypothetical positions of the fluorescent
    labels of proteins A and B. Scale bar: 200\,nm \textbf{c:} Computed
    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
    for the green marker.}
  \label{fig:sicm-and-light-resolution}
\end{figure}
In all stable structures in the recordings (highlighted by the dashed lines)
at least one group of three protrusions arranged in a line are observable. To
exemplify the impact of the limited resolution of light microscopy, assume,
without any biological support, that such a complex is comprised of two
different proteins A and B, which float in the plasma membrane until they form
the complex. In the complex, protein A is located at the first and last
position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
protein B on the central spot (green arrows in
Fig.~\ref{fig:sicm-and-light-resolution}a). Further, assume that the two
different proteins have been labelled by two different fluorescent markers
(the positions of the markers are indicated by the magenta and green dots in
Fig.~\ref{fig:sicm-and-light-resolution}b) and a correlating light microscopic
image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}c) to analyze
the molecular composition of the stable structures.
